{\helveticaitalic{Supplementary Material}}

### 2022-03-30 tex/supplementary.tex
Update a bunch of tex files

\documentclass[utf8]{frontiers_suppmat} % for all articles
\usepackage{url,hyperref,lineno,microtype}
\usepackage[onehalfspacing]{setspace}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{xr}
\externaldocument{draft}

@@

@@

Note that applying conventional methods of numerical continuation is not straightforward for our model, as the discontinuous resets in \cref{eq:s-reset} and~\eqref{eq:d-reset} make the root finding challenging~\citep[e.g. see][ for continuation methods]{kuznetsov2004}.

>>>>

\documentclass[utf8]{frontiers_suppmat} % for all articles
\usepackage{url,hyperref,lineno,microtype}
\usepackage[onehalfspacing]{setspace}
\usepackage{cleveref}
\usepackage{graphicx}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{interval}
\intervalconfig{soft open fences}
\usepackage{xr}
\externaldocument{manuscript}

@@

\graphicspath{{../figures}}

@@

\section{Numerical validation of constant ISI assumption}
\label{sec:tauk}
% TODO Double-check that you've addressed all of the reviewers concerns here.
% TODO Write caption
To study the effect of the synaptic time constant $\tau_\kappa$ on consecutive $ISI$s of the active cell we consider a single cell that is inhibited by an exponentially decaying synaptic conductance $g$:
\begin{align}
	\label{eq:dotv}
	\dot v & = f(v, w) - g(v - v_{s}), \\
	\label{eq:dotw}
	\dot w & =h(v, w),                 \\
	\label{eq:dotg}
	\dot g & = -g/\tau_{\kappa},
\end{align}
where functions $f$ and $h$ come from \cref{eq:f,eq:h}.
We assume that the cell is released and fires its first spike at time $t=0$.
We therefore initialise $v$ at the firing threshold $v_{\theta}$, $w$ at its nullcline, and
the $g$ at the release conductance $g^{\star}$, respectively:
\begin{align}
	v(0) & = v_{\theta}, \\
	w(0) & = v(0),       \\
	g(0) & = g^{\star}.
\end{align}
We vary $\tau_{\kappa}$ and integrate the system numerically to record consecutive $ISI$s.

\Cref{fig:tauk-vs-ISI} shows the curves for the first ($ISI_{1}$), second ($ISI_{2}$), and third ($ISI_{3}$) inter-spike-intervals for values $\tau_{\kappa} \in \interval[open left]{0}{800}$.
These results suggest that for $\tau_\kappa \leq 100$ we have $ISI_i \approx T$, that is, inhibition $g$ decays sufficiently fast for its effect on the spiking period to be negligible.
For $\tau_\kappa > 100$ the first $ISI_{1}$ becomes increasingly longer with $\tau_{\kappa}$, moreover the effect of the inhibition propagates to the subsequent $ISI_{2}$ and $ISI_{3}$, suggesting that for a too slow synaptic time constant the assumption $ISI \approx T$ is not suitable.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\textwidth]{tauk-vs-ISI}
	\caption{Voltage traces of both cells of numerically stable solutions for increasing
		values of the coupling strength $\gbar$ (increasing top to
		bottom).~\label{fig:tauk-vs-ISI}}
\end{figure}

% TODO
% **Note of caution**: Our ICs might be inaccurate for very large $\tau_\kappa$ , since then $w(0) \approx w_\infty(g^\star)$ will be likely violated.

% \section{Irregular solutions}
% Even
